Proposed Solution

### 2017-01-25 CAV17/secs/motiv.tex

In this section we illustrate capabilities of \app by 
using several real-world misconfiguration examples. 
These examples are non-trivial configuration errors
that were reported on StackOverflow~\cite{stackoverflow},
a popular forum for programmers and administrators.

>>>>

In this section we illustrate capabilities of \app by 
using several real-world misconfiguration examples. 
These examples are sophisticated configuration errors
that were reported on StackOverflow~\cite{stackoverflow},
a popular forum for programmers and administrators.

### 2017-01-25 CAV17/secs/postanal.tex

\section{Post Analysis}

@@

Accessibility of the Rule Graph is a useful property of the association 
rule learning technique applied by \app.
While it is possible to analyze the models from other machine learning techniques such as neural networks~\cite{lei2016rationalizing} and
conditional random fields~\cite{raychev2015predicting}, these analyses require a deep knowledge of the applied techniques.
In contrast the Rule Graph is a relatively simple, yet information rich, representation of the learned model.
The following section provides a precise definition of the Rule Graph
and demonstrates useful metrics we derive for the purposes of ranking reported errors
and complexity analysis.

>>>>

\section{Rule Graph Analysis}
\label{sec-post}

@@

Accessibility of the Rule Graph is a useful property of the association 
rule learning technique applied by \app.
While it is possible to analyze the models from other machine learning techniques, such as neural networks~\cite{lei2016rationalizing} and
conditional random fields~\cite{raychev2015predicting}, these analyses require a deep knowledge of the applied techniques.
In contrast the Rule Graph is a relatively simple, yet information rich, representation of the learned model.
The following section provides a precise definition of the Rule Graph
and demonstrates useful metrics we derive for the purposes of ranking reported errors
and complexity analysis.
